
\blandscape

EID
===

EID: PMTCT_EID (N)
------------------

**PMTCT_EID:** Number of infants who had a first virologic HIV test
(sample collected) by 12 months of age during the reporting period.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("EID-PMTCT_EID (N)-C-G-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("EID-PMTCT_EID (N)-C-G-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   ${\bf \leq 02 mo}$ [PMTCT_EID.N.2.T]

-   ${\bf 02-12 mo}$ [PMTCT_EID.N.12.T]

### Instructions

The PMTCT_EID indicator measures the extent to which HIV-exposed infants
receive a first virologic HIV test to determine their HIV status by
either 2 months or 12 months of age. Ideally, 80% of infants should be
tested within the first two months, and 90-95% within the first twelve
months.

1.  Review and adjust the assumptions for "Targeted % HIV exposed
    infants tested by 2 mo (%)" and "Targeted % HIV exposed infants
    tested by 12 mo (inclusive of tested by 2 mo) (%)". These will be
    set at a default of 80% and 95%, respectively. Red highlights
    indicate percentages over 100%; yellow highlights indicate
    percentages less than these default percentages.

2.  Review the Estimated number of infants born to HIV-positive women.
    In absence of granular, reliable, widespread data to estimate rates
    of multiple births, still births, or infant mortality, this
    statistic is approximated using the total number of HIV-positive
    women presenting to ANC (column "Total PMTCT: Positives (From ANC1 &
    Post ANC1)" of the PMTCT tab). For more information about the
    assumptions underlying this data, see the section of this User Guide
    about the PMTCT tab.

3.  Review modeled targets for "$\leq$ 02 mo" and "02 - 12 mo" PMTCT_EID,
    which are based on the proportions of HIV exposed infants (reflected
    in step 2) to be tested by 2 months and by 12 months (set in step
    1). Return to steps 1 and 2 to make adjustments to the assumptions
    driving these two sets of targets.

EID: PMTCT_HEI_POS (N)
----------------------

**PMTCT_HEI_POS (N):** Number of HIV-infected infants identified in the
reporting period, whose diagnostic sample was collected by 12 months of
age.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("EID-PMTCT_EID (N)-H-K-1-2", "latex")

schema_table("EID-PMTCT_EID (N)-L-N-2-2", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("EID-PMTCT_EID (N)-H-N-1-1", "html")
```


### DATIM Import

No data points will be imported into DATIM from this section.

### Instructions

1.  For historical context, review FY20 results for Estimated Positivity
    Rates both for infants tested before 2 months old, and those tested
    between 2 and 12 months old. These data reflect data as reported
    currently in DATIM.

2.  Review and adjust assumptions for FY22 projections of Estimated
    Positivity Rates both for infants tested before 2 months old, and
    those tested between 2 and 12 months old. These data default to the
    same as those rates set in step 1, but can be adjusted as needed.
    Red highlights indicate percentages over 100% or less than 0%;
    yellow highlights indicate percentages that differ from those set in
    step 1.

3.  Review Targeted proportion of HIV-infected infants linked to ART.
    This rate is locked in step with ART Linkage Rates set on the
    Cascade Tab, which default to 95%; return to that tab to adjust this
    rate, though note that this will alter linkage rates across all
    modalities.

4.  Review "Total HIV infected infants identified" which will be the
    product of PMTCT_EID set in the previous section, multiplied by the
    Estimated Positivity Rates set in this section, summed across both
    PMTCT_EID age disaggregates. Please see below for a detailed formula
    of the calculation.

5.  Lastly, "HIV infected infants confirmed initiated ART" will take
    "Total HIV infected infants identified" that was just set and
    multiply it by the targeted link to ART of 95%.

### PMTCT_HEI_POS (FY22)

To calculate the total number of HIV-infected infants to be tested and
identified, the Data Pack uses the following formula, rounding to the
nearest integer:

\begin{center} $PMTCT\_ HEI\_ POS.T\  = \ (PMTCT\_ EID.N.2.T\  \times \ PMTCT\_ HEI\_ POS.2.Yield.T)\  + \ (PMTCT\_ EID.N.12.T\  \times PMTCT\_ HEI\_ POS.12.Yield.T)\ $ \end{center}

\elandscape

\newpage

