---
editor_options: 
  markdown: 
    wrap: 72
---

\blandscape

# CASCADE

The Cascade Tab allows DataPack users to view and set the overall
contour of their treatment and testing program across both geography and
population. The Cascade tab of the COP22 DataPack saw the most changes
across all tabs from the COP21 version. New Section 7 COP guidance will
begin setting the Cascade from Program Viral Load Suppression. This
starting point will allow for country team users to build up a full
cascade that will provide insight into VLS, VL Testing and how this will
translate into determining the new on treatment and those returning to
treatment. It will provide a full picture of the treatment ecosystem and
the way in which countries understand if they will achieve 85% coverage
across all three Cascades. This will allow countries that are at or
close to Epi Control to better approach the understanding of how they
will continue to sustain their 95-95-95 goals. This approach will put a
greater emphasis on the Coverage Cascade as the driver of the target
setting process, a direct shift from the past 5 years that have focused
on the first two Cascades, and paint a picture of both VL to gap in
Treatment and Testing.

This tab also links heavily with many other tabs of the Data Pack,
including the PMTCT, TB, EID, VMMC, KP, HTS, CXCA, HTS_RECENT, and
TX_TB_PREV tabs. By beginning with the Cascade tab, moving through each
of these other tabs, and continually returning to the Cascade tab to
monitor and iteratively adjust the overall program plan, Country Teams
can both retain a cohesive and intentional strategy across program area,
geography, and population, as well as anchor this strategy in data and
the realities of past performance.

## Host Country Context

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-Host Country Context-F-I-1-5", "latex")

schema_table("Cascade-Host Country Context-J-M-2-5", "latex")

schema_table("Cascade-Host Country Context-N-P-3-5", "latex")

schema_table("Cascade-Host Country Context-Q-S-4-5", "latex")

schema_table("Cascade-Host Country Context-T-Y-4-5", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-Host Country Context-F-Y-1-1", "html")
```

For those leveraging UNAIDS Spectrum estimate exports for the Data Pack,
once these have been loaded into the Spectrum tab of the Data Pack, this
first portion of the Cascade tab will automatically update to reflect
these estimates.

In specific, the Host Country Context section of the Cascade tab
provides space for reflecting estimates from either Spectrum or an
alternative approved source for the following data:

-   **Host Country Estimated Population (FY22)** $POP\_EST.T\_1$:
    Estimated population, projected as of September 2022.

-   **Host Country Estimated PLHIV (FY22)** $PLHIV.T\_1$: Estimated
    number of people living with HIV, projected as of September 2022.

-   **Host Country Estimated HIV Prevalence (FY22) (%)**
    $HIV\_PREV.T\_1$: Estimated HIV Prevalence, projected as of
    September 2022.

-   **Host Country Projected Incidence Rate (FY22) (%)**
    $Incidence\_SUBNAT.Rt.T\_1$:

-   **Host Country Projected New Infections (FY23)**
    $NEW\_INFECTIONS\_SUBNAT.T\_1$:

-   **Host Country PLHIV Diagnosed (FY22)** $DIAGNOSED\_SUBNAT.T\_1$:

-   **Host Country Observed TX_CURR_SUBNAT (FY21)**
    $TX\_CURR\_SUBNAT.R$: Observed/actual total number of PLHIV
    receiving ART as of September 2021.

-   **Host Country Estimated TX_CURR_SUBNAT (FY22)**
    $TX\_CURR\_SUBNAT.T\_1$: Estimated number of PLHIV receiving ART,
    projected as of September 2022.

-   **Host Country Est. ART Patients Tested for VLS (FY22)**
    $VL\_TESTING\_SUBNAT.T\_1$: Estimated number of ART Patients who
    have been tested, PEPFAR projected as of September 2022.

-   **Host Country Estimated Virally Suppressed ART Patients
    (FY22)**$VL\_SUPPRESSION\_SUBNAT.T\_1$: Estimated PLHIV on ART and
    virally suppressed, projected as of September 2022.

### DATIM Import

As part of the DataPack approval process, all of the above FY22
projected estimates will be uploaded into DATIM and replace any
preexisting estimates for these indicators that may have already been
entered in DATIM, perhaps via Data Pack upload during COP21.

### Instructions

1.  If using UNAIDS Spectrum as the source for these data:

    a.  Review the above columns to confirm that data has been correctly
        linked with the Spectrum tab. You may consider using filter
        drop-down menus to quickly inspect for any non-numeric,
        negative, or invalid data.

    b.  Review Relative Standard Error values to identify any estimates
        with a Relative Standard Error of more than or equal to 20. See
        the section below for additional instructions.

2.  If not using UNAIDS Spectrum as the source for these data, see the
    below section.

3.  Confirm that no data has been entered against Military Organization
    Units. See below for more explanation.

### Leveraging Alternatives to Spectrum

In general, all data for the above should use UNAIDS Spectrum as their
source. However, there may be cases where either a more up to date or
reliable source exists, or where data may not be fully available from
UNAIDS Spectrum. In these cases, Country Teams may request approval from
their PPM and a DUIT Liaison to use an alternative data source. Be sure
to request and document this approval before deciding not to use
Spectrum as the source for your Data Pack host country estimates, as
well as what source is approved for use in its place. This is true for
all cases where you may need to leverage an alternative to Spectrum,
whether for an entire indicator, or for a specific geography or
population.

For those not leveraging Spectrum to provide host country context
estimates, you may paste estimates from other approved sources into this
section of the Cascade tab by overwriting the formulas currently in
these columns. Due to hidden Relative Standard Error columns between the
various estimate columns, it is recommended you paste this data in one
column at a time, rather than in bulk. It may also reduce technical
issues to first copy geographic data in the SNU1, PSNU, Age, and Sex
columns into a separate spreadsheet, then use Excel lookup functions to
add estimates data against the correct geographies and populations, and
then return to pasting data into the original Cascade tab column by
column.

### Relative Standard Errors

Data exported from UNAIDS Spectrum will also come with a series Relative
Standard Errors for each data point, both at the District level as well
as the Age/Sex-specific level. Along with the data points listed above,
Relative Standard Errors for each will also automatically be populated
in the Cascade tab from data loaded into the Spectrum tab. While
initially, these Error columns will be hidden, you may inspect these
values by unhiding these columns. Based on these Relative Standard
Errors, data points in related columns will be color-coded to indicate
the relative uncertainty of each specific data point along the following
ranges:

-   Red: Relative Standard Error of 40 or greater.

-   Yellow: Relative Standard Error of less than 40, but more than or
    equal to 20.

-   Green: Relative Standard Error of less than 20.

While these error estimates are available as a reference as teams
formulate targets, red or yellow highlighting may not always mean a data
point should be thrown out, nor is it the case that all green values
should be taken at face value. Either way, consider these error
estimates as helpful guideposts in interpreting the contextual meaning
and data quality of data provided via UNAIDS Spectrum output.

If, in reviewing Relative Standard Error values, the uncertainty
interval of an estimate appears to be concerning, consider the following
next steps:

1.  Raise and discuss the issue with your PPM and DUIT Liaison.

2.  Communicate concerns to assigned UNAIDS liaisons and discuss
    appropriate methods for improving or better understanding data
    quality for the data points in question.

### Host Country Estimates for Military Organization Units

Due to issues of political sensitivity and national security, estimates
for the above indicators should not be entered against Military
Organization Units. Any case where this does occur will be flagged in
the Data Pack Self-Service App, and removed during DATIM import.

## Host Country Cascade

With the pivot to setting the Cascade from a Program Viral Load
Suppression rate this section will provide users with further insight
into all three Cascades. This approach will also put a greater emphasis
on the Coverage Cascade as the driver of the target setting process, a
direct shift from the past 5 years that have focused on the first two
Cascades.

## PEPFAR Programmatic Cascade

This section has been added in an effort to further highlight the
progress being made as well as painting a picture of both VL to gap in
Treatment and Testing. These columns will be populated with FY21 Results
and FY22 Targets from DATIM and will serve as further reference as users
set targets throughout the Cascade tab.

## Cascade: PEPFAR FY21 Cascade (Observed and Planned)

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-PEPFAR FY21 Cascade (Observed)-Z-AD-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-PEPFAR FY21 Cascade (Observed)-Z-AD-1-1", "html")
```

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-PEPFAR FY22 Cascade (Planned)-AE-AI-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-PEPFAR FY22 Cascade (Planned)-AE-AI-1-1", "html")
```

This Section of the Cascade tab has been added to give users an insight
into key Cascade FY21 Results and FY22. Users can refer to these past
indicator results and targets to aid in the target setting and review
process. The following are included as both FY21 Results and FY22
Targets in these two sections:

-   New Positives (This includes both HTS_TST_POS & PMTCT_HEI_POS)

-   TX_NEW

-   TX_CURR

-   TX_PVLS (D)

-   TX_PVLS (N)

## Cascade: VL_SUPPRESSION_SUBNAT

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-VL_SUPPRESSION_SUBNAT-AJ-AN-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-VL_SUPPRESSION_SUBNAT-AJ-AN-1-1", "html")
```

This section of the Cascade tab builds upon the preceding Host Country
Context and the PEPFAR Programmatic Cascade sections to arrive at an
analysis of gap to VL coverage by geography and population. This
analysis, in concert with projected goals for VL to gap in TX and VL gap
to testing to be attained by the end of FY23, then helps DataPack users
simulate the required net new amount of individuals (those added less
those lost to follow-up) to be added to host country ART totals.

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **Targeted Host Country VL_SUPPRESSION_SUBNAT (FY23)**
    $VL\_SUPPRESSED.T$

### Instructions

1.  Review historic PEPFAR PVLS_NET_NEW and Coverage of Host Country
    PopVLS data to understand existing trends and status of Host Country
    VLS by geography and population.

2.  Review estimates of PEPFAR Coverage of Host Country
    VLS_NET_NEW_SUBNAT and adjust as necessary. See below for additional
    information.

3.  Review baseline Host Country Estimated PopVLS Rate Coverage.

4.  Review and adjust Targeted Host Country PopVLS Rate Coverage. See
    below for additional information

5.  Review resulting **Targeted Host Country VL_SUPPRESSION_SUB NAT**
    and **Targeted Host Country VLS_NET_NEW_SUBNAT**. See below for
    additional information.

### PEPFAR Coverage of Host Country VLS_NET_NEW_SUBNAT

In the next section of the Data Pack, the VLS_NET_NEW_SUBNAT determined
in this section will be used to estimate necessary PEPFAR
TX_PVLS_NET_NEW.

To estimate PEPFAR's contribution to total TX_NET_NEW_SUBNAT in the
country, the Data Pack compares PEPFAR's most recent APR results for
TX_CURR against the observed host country TX_CURR_SUBNAT results ---
sourced from UNAIDS Spectrum, or an alternative approved source, as
described in the Host Country Context section prior to this --- for the
same time period.

While the behavior of PEPFAR and Host Country TX_CURR may differ from
that of TX_NET_NEW, this gives a baseline from which to begin, and
ultimately you may adjust this baseline in the green column titled
"**PEPFAR Coverage of Host Country TX_NET_NEW_SUBNAT (FY22) (%)**" to
more accurately reflect the likely reality of PEPFAR's contribution to
TX_NET_NEW_SUBNAT.

### Targeted Host Country PopVLS Coverage

One of the most pivotal data points in the Data Pack is the baseline
estimate of Host Country PopVLS Coverage. To calculate the estimated
Host Country PopVLS Coverage for FY22 (i.e., projected as of September
2022), the Data Pack uses the following formula:

\begin{center}

$\frac{Host\ Country\ Est.\ Virally\ Suppressed\ ART\ Patients\ (FY22)}{Host\ Country\ Est.\ PLHIV\ (FY22)}$ 

\end{center}

In the case that PEPFAR's reported TX_CURR results for FY20 exceed the
reported Host Country Observed TX_CURR_SUBNAT for FY20, the following
function will be used to calculate ART Coverage instead of the above:


\begin{center} $\frac{PEPFAR\ TX\_ CURR\ (FY20\ Results)}{Host\ Country\ Est.\ PLHIV\ (FY21)}$ \end{center}

Reviewing and understanding the PopVLS Coverage estimate arrived at in
this column is critical for much of the rest of the Data Pack. In
particular, this column is later instrumental in determining the
following key data points:

-   Host Country VL_SUPPRESSION_SUB NAT

-   Host Country VLS_NET_NEW_SUBNAT

-   PEPFAR TX_PVLS

-   PEPFAR TX_NEW

-   PEPFAR TX_CURR

-   PEPFAR TX_CURR_SUBNAT

-   PEPFAR HTS_TST totals

-   PEPFAR HTS_INDEX

After reviewing data in this column, examine the next column, **Targeted
Host Country PopVLS Coverage (FY22) (%)**. In line with the UNAIDS
95-95-95 goals, this column defaults to 95%, reflecting that since the
denominator in the Data Pack calculation is Host Country Estimated PLHIV
instead of only those PLHIV who know their HIV Status, this column
should be the equivalent of:

\begin{center} $(95\%\ of\ PLHIV\ know\ their\ HIV\ status)\ \  \times \ (95\%\ of\ PLHIV\ who\ know\ their\ status\ are\ on\ ART)$ \end{center}

However, in cases where baseline PopVLS Coverage may be greater than
95%, baseline PopVLS Coverage will be used instead of 95%.

No matter the starting default for Targeted Host Country PopVLS
Coverage, you may adjust this target to fit the realities of your
country context, and the strategy of your treatment program. It may also
be helpful to return to this column to iteratively adjust it as you
proceed through the next few sections of the Data Pack.

NOTE: The Data Pack will not prevent situations resulting in ART
coverage exceeding 100% in a given PSNU, but will flag these cases in
yellow to highlight when it occurs. Given that these may be a common
occurrence in cases of urban PSNUs, they are allowable in the Data Pack,
though should be coordinated with PPMs and DUIT Liaisons.

### Targeted VL_SUPPRESSION_SUBNAT and VLS_NET_NEW_SUBNAT

Targeted Host Country VL_SUPPRESSION_SUBNAT (FY23) is set as follows
(rounded to the nearest integer):


\begin{center} ${TX\_ CURR\_ SUBNAT}_{t}\  = \ \text{PLHIV}_{t - 1}\  \times \ \ Targeted\ Host\ Country\ ART\ Coverage$ \end{center}

Based on this target, Targeted Host Country VLS_NET_NEW_SUBNAT (FY23) is
set as follows:


\begin{center} ${TX\_ NET\_ NEW\_ SUBNAT}_{t}\  = \ {TX\_ CURR\_ SUBNAT}_{t}\  - \ {TX\_ CURR\_ SUBNAT}_{t - 1}$ \end{center}

In performing this calculation, the Data Pack also compares projected
FY21 Host Country TX_CURR_SUBNAT values reported in the Data Pack
against FY21 PEPFAR TX_CURR targets as contained in DATIM. If PEPFAR
targets exceed Host Country projected TX_CURR_SUBNAT values for FY21,
Targeted Host Country TX_NET_NEW_SUBNAT for FY22 is instead calculated
as follows:


\begin{center} ${TX\_ NET\_ NEW\_ SUBNAT}_{t}\  = \ {TX\_ CURR\_ SUBNAT}_{t}\  - \ \frac{{PEPFAR\ TX\_ CURR}_{t - 1}}{{PEPFAR\ Coverage\ of\ Host\ Country\ TX\_ CURR\_ SUBNAT\ }_{t - 1}}$ \end{center}

For those using Spectrum as their source for TX_CURR_SUBNAT projections,
this scenario is rare because of incorporation of PEPFAR TX_CURR targets
into Spectrum modeling. However, it may be possible to see discrepancies
between PEPFAR TX_CURR targets and modeled TX_CURR_SUBNAT values,
especially as Country Teams continue to make necessary OPU target
changes. In this case, as well as in cases where data from alternative
sources may exhibit discrepancies, the Data Pack takes this into account
and adjusts to maintain reasonable Host Country TX_NET_NEW_SUBNAT
targets as best as possible.

### Gap to Coverage Analysis for Military Organization Units

Due to sensitivities around ART coverage estimates for Military
organization units and populations, this data will not be reflected here
in the Data Pack. Country Teams should coordinate closely with
Department of Defense liaisons who will perform a similar analysis based
on available data sources and then directly paste resulting TX_CURR
targets into the Data Pack against the \_Military organization unit,
overwriting the formulas present in the TX_CURR column described in the
next section.

## Cascade: TX_PVLS (N)

**TX_PVLS (N):** Number of ART patients with suppressed VL results
(\<1,000 copies/mL) documented in the medical or laboratory results/LIS
within the past 12 months.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-TX_PVLS (N)-AU-AW-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-TX_PVLS (N)-AU-AW-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **TX_PVLS (N): Routine (FY23)** $TX\_PVLS.N.Routine.T$

### Instructions

1.  Review PMTCT_HEI_POS Virally Suppressed which will be set in the EID
    tab for \<1 yr age group and pulled into the Cascade tab. .

2.  Review and adjust Targeted Host Country VLS_NET_NEW_SUBNAT for FY23
    from the previous section. ((This is defaulted at 95%, reflective of
    UNAIDS 95-95-95 goals))\*.

3.  Review and adjust targeted PEPFAR Coverage of Host Country
    VLS_NET_NEW_SUBNAT (FY23). This is defaulted to match the PEPFAR
    Coverage of Host Country PopVLS (FY22) set in the VLS_NET_NEW_SUBNAT
    section of the Cascade tab, but can be altered as appropriate.

4.  Review targeted TX_PVLS_NET_NEW for routine viral load testing. See
    below for additional information.

5.  Review targeted VL_SUPPRESSION_SUBNAT. See below for additional
    information.

6.  Review the Targeted Host Country VL Suppression Rate (FY22)
    resulting from modeled Host Country VL_SUPPRESSION_SUBNAT and return
    to previous sections and columns within this section to adjust
    contributing assumptions. See below for further information.

### TX_PVLS (N): Routine (FY23)

Similar to TX_PVLS Denominator, COP21 targets for the Numerator for this
indicator are set only for Routine Viral Load testing.

Within the Data Pack, TX_PVLS Numerator targets for Routine Viral Load
Testing are set as follows, rounded to the nearest integer:

\begin{center} ${TX\_ PVLS.N.Routine}_{t}\  = \ {TX\_ PVLS.D.Routine}_{t}\  \times \ \text{Targeted\ VL\ Suppression\ Rate}_{t}$ \end{center}

### VL_SUPPRESSION_SUBNAT (FY22)

In conjunction with allowing import and update of FY21 targets in DATIM
for VL_SUPPRESSION_SUBNAT, the Data Pack also allows import of FY22
targets for this indicator. These are modeled within the Data Pack as
follows, rounded to the nearest integer:


\begin{center} ${VL\_ SUPPRESSION\_ SUBNAT}_{t}\  = \ \frac{{TX\_ PVLS.N.Routine}_{t}}{{PEPFAR\ Coverage\ of\ Host\ Country\ VL\_ SUPPRESSION\_ SUBNAT}_{t}}$ \end{center}

## Cascade: TX_PVLS (D)

**TX_PVLS (D):** Number of ART patients with a Viral Load (VL) result
documented in the medical or laboratory records/laboratory information
system (LIS) within the past 12 months.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-TX_PVLS (D)-AM-AO-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-TX_PVLS (D)-AM-AO-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **TX_PVLS (D): Routine (FY23)** $TX\_PVLS.D.Routine.T$

### Instructions

1.  Review and adjust assumptions for the proportion of TX_PVLS (D)
    projected to be eligible for viral load testing during the coming
    Fiscal Year. The default assumption is 95%, reflecting the MER 2.6
    guidance that individuals must have been on ART for at least 3
    months in order to be eligible for viral load testing. Red
    highlighting in this column indicates values over 100%, and yellow
    highlighting values below 70%.

2.  Review targeted TX_PVLS (D) for routine viral load testing. See
    below for additional information.

### TX_PVLS (D): Routine (FY23)

While MER 2.6 allows for both Routine and Targeted Viral Load testing,
only Routine Viral Load testing will be targeted as part of COP 22
planning.

Within the Data Pack, TX_PVLS Denominator targets for Routine Viral Load
Testing are set as follows, rounded to the nearest integer:


\begin{center} ${TX\_ PVLS.D.Routine}_{t}\  = \ \lbrack({TX\_ NEW}_{t}\  \times \ {\%\ TX\_ NEW\ eligible\ for\ VL\ Testing}_{t})\  + \ {TX\_ CURR}_{t - 1}\rbrack\  \times \ {\%\ Access\ to\ VL\ Testing}_{t}$ \end{center}

Note that no retention rates are applied against either TX_NEW~t~ nor
TX_CURR~t-1~ , reflecting the goal that all individuals on ART should be
tested for viral load suppression, no matter whether they may in the
future --- even within the same Fiscal Year --- be lost to follow-up.

## Cascade: VLT Coverage

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-VLT Coverage-AV-AY-1-4", "latex")

schema_table("Cascade-VLT Coverage-AZ-BC-2-4", "latex")

schema_table("Cascade-VLT Coverage-BD-BG-3-4", "latex")

schema_table("Cascade-VLT Coverage-BH-BL-4-4", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-VLT Coverage-AV-BL-1-1", "html")
```

### DATIM Import

No Targets will be imported to DATIM from this section.

### Instructions

1.  Review

## Cascade: TX_NEW

**TX_NEW:** Number of adults and children newly enrolled on
antiretroviral therapy (ART). $Part 1 of 2$

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-TX_NEW-BM-BN-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-TX_NEW-BM-BN-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **TX_NEW (FY22)** $TX\_NEW.T$

### Instructions

1.  Review the column, % TX_NEW Eligible for VL Test (FY23) (%). This is
    defaulted to 70%, but can be adjusted as necessary. See below for
    additional instructions. Red highlighting will identify cases where
    these may be set above 100%, and yellow highlighting those cases
    were set below 70%.

2.  Review targeted % of eligible w/ access to VL testing (FY23) (%).
    This is defaulted to 100%, but can be adjusted as necessary. Red
    highlighting will identify cases where these may be set above 100%,
    and yellow highlighting those cases were set below 100%.

3.  Review historic data for TX_NEW Results and Targets for reference
    from the PEPFAR Programmatic Cascade section.

4.  Review FY23 TX_NEW targets and return to previous sections to adjust
    assumptions and modeling decisions as necessary. See below for
    additional information.

### Proportion of TX_NET_NEW from New ART Initiation

New to the COP21 Data Pack, this column allows for several scenarios
that may impact how PEPFAR TX_NET_NEW translates to TX_NEW targets. The
most common of these scenarios include:

-   Cases where TX_RTT may contribute in part to TX_NET_NEW, requiring a
    reduction in how much TX_NET_NEW is converted into targets for
    TX_NEW. While TX_RTT targets are not set in the COP21 Data Pack,
    this column does allow for the possibility that some amount of
    TX_RTT may be an unavoidable part of a cohesive, effective treatment
    strategy.

-   Cases where PEPFAR may be absorbing or beginning support for an
    existing Treatment cohort from a non-PEPFAR partner, such as the
    Global Fund to Fight AIDS, Tuberculosis, and Malaria.

Red highlighting will identify cases where this column is set above
100%, and yellow highlighting where it is set below 100% for review
purposes.

As described below, any adjustments to this column will directly impact
the target set for TX_NEW. As such, be sure to receive approval from
your PPM and DUIT Liaison for any changes to this column, and be
prepared to explain and justify the rationale for these changes as
necessary.

It is important to note that even in cases where TX_NET_NEW may be zero,
it still may be necessary to add individuals into the Treatment cohort,
whether from new initiation or otherwise, to compensate for those
individuals lost to follow up. In these scenarios, the proportion
described in this section will apply to this non-zero total of
individuals to be added to the Treatment cohort. In other words, the
Proportion of TX_NET_NEW from New ART Initiation can be described as:


\begin{center} ${Proportion\ TX\_ NET\_ NEW\ from\ New\ ART}_{t}\  = \ \frac{{(TX\_ NEW}_{t}) \times ({Ret.\ Rate:\ New\ on\ ART}_{t})}{\text{Individuals\ to\ be\ added\ to\ Treatment\ Cohort}_{t}}$ \end{center}

As explained above, the number of individuals to be added to the
Treatment Cohort may not be the same as TX_NET_NEW in all cases due to
Retention Rates among the prior year Treatment Cohort. In other words,


\begin{center} $\text{Individuals\ to\ be\ added\ to\ Treatment\ Cohort}_{t}\  = \ {TX\_ NET\_ NEW}_{t}\  + \ ({TX\_ CURR}_{t - 1})(1 - {Ret.\ Rate:\ Already\ on\ ART}_{t})$ \end{center}

and given that


\begin{center} ${TX\_ NET\_ NEW}_{t}\  = \ {TX\_ CURR}_{t} - {TX\_ CURR}_{t - 1}$ \end{center}

therefore,


\begin{center} $\text{Individuals\ to\ be\ added\ to\ Treatment\ Cohort}_{t}\  = \ {TX\_ CURR}_{t}\  - \ ({TX\_ CURR}_{t - 1}\  \times \ {Ret.\ Rate:\ Already\ on\ ART}_{t})$ \end{center}

All this means that the Proportion of TX_NET_NEW from New ART can be
framed as follows:


\begin{center} ${Proportion\ TX\_ NET\_ NEW\ from\ New\ ART}_{t}\  = \ \frac{{(TX\_ NEW}_{t}) \times ({Ret.\ Rate:\ New\ on\ ART}_{t})}{{TX\_ CURR}_{t}\  - \ ({TX\_ CURR}_{t - 1}\  \times \ {Ret.\ Rate:\ Already\ on\ ART}_{t})}$ \end{center}

See below to see how this affects TX_NEW targeting.

### TX_NEW (FY22)

For those one year old and older, PEPFAR TX_NEW targets for FY23 will be
set using the formula laid out above for Proportion of TX_NET_NEW from
New ART, solving for TX_NEW, with each component and the total rounded
to the nearest integer:


\begin{center} ${TX\_NEW}_{t}\  = \ \frac{\lbrack{TX\_ CURR}_{t} - \ ({TX\_ CURR}_{t - 1} \times {Ret.\ Rate:\ Already\ on\ ART\ }_{t})\rbrack \times {Proportion\ TX\_ NET\_ NEW\ from\ New\ ART}_{t}}{{Ret.\ Rate:\ New\ on\ ART\ }_{t}}$ \end{center}

See below for additional information about how TX_NEW targets are set
among Infant populations.

### Setting TX_NEW Targets among Infant Populations

Based upon rationales explained in previous sections above, TX_NEW
targets for infant populations will simply reflect TX_NET_NEW values
determined in the TX_CURR section of the Cascade tab. Refer to that
section for more information about how to adjust TX_NEW targets for
infant populations.

## Cascade: TX_CURR

**TX_CURR:** Number of adults and children currently receiving
antiretroviral therapy (ART).

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-TX_CURR-BO-BS-1-1", "latex")

```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-TX_CURR-BO-BS-1-1", "html")

```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **TX_CURR (FY23)** $TX\_CURR.T$

### Instructions

1.  For ages one and older:

    a.  Compare TX_NET_NEW (FY22) against TX_NET_NEW (FY21) from the
        TX_NET_NEW_SUBNAT section (described above) to identify any
        geographies or populations where previous modeling decisions
        pertaining to FY22 Targeted Host Country TX_CURR_SUBNAT, FY22
        Targeted Host Country TX_NET_NEW_SUBNAT, PEPFAR Coverage of Host
        Country TX_NET_NEW_SUBNAT, and/or FY22 Targeted Host Country ART
        Coverage may be leading to over targeting of FY22 PEPFAR
        TX_NET_NEW. Adjust assumptions in previous sections as
        necessary. (See below for additional information about
        TX_NET_NEW_SUBNAT targeting.)

    b.  Review FY22 TX_CURR targets to identify and resolve any issues
        pertaining to previous modeling assumptions or decisions. (See
        below for additional information about TX_CURR targeting.)

2.  For infant populations:

    a.  Continue moving on through the remainder of the Cascade tab,
        taking special care to review the PMTCT and EID tabs of the Data
        Pack, reconciling issues with overall Testing Rationalization
        along the way.

    b.  Once modeling of PMTCT, EID, and HEI_POS targets is complete,
        return to this section of the Data Pack to review how HEI_POS
        targets on the EID tab link to TX_CURR on the Cascade tab. See
        below for additional information.

### TX_NET_NEW (FY23)

For those one year old and older, TX_NET_NEW targets for FY22 are set in
the Data Pack as follows, rounded to the nearest integer:


\begin{center} ${TX\_ NET\_ NEW}_{t}\  = \ {TX\_ NET\_ NEW\_ SUBNAT}_{t}\  \times \ {PEPFAR\ Coverage\ of\ Host\ Country\ TX\_ NET\_ NEW\_ SUBNAT\ }_{t}\ $ \end{center}

For a description of how TX_NET_NEW is modeled for infants, see section
below.

### TX_CURR (FY23)

For those one year old and older, TX_CURR targets for FY22 are set in
the Data Pack as follows:


\begin{center} ${TX\_ CURR}_{t}\  = \ {TX\_ CURR}_{t - 1}\  + \ {TX\_ NET\_ NEW}_{t}$ \end{center}

For a description of how TX_CURR is modeled for infants, see section
below.

### Setting TX_CURR Targets among Infant Population Groups

Because infants enter the Treatment cohort through a distinctly separate
method than the rest of the population, and also given that all infants
in the previous year's Treatment cohort will entirely shift into the 1-4
year old age group leaving none to carry over into the next year's
cohort, TX_CURR targets for this population do not follow the chain of
logic described thus far. Instead, TX_CURR targets for infants are
driven by the model for EID testing, which is in turn based on the model
for PMTCT testing and treatment.

As described above in the Instructions section for this tab, upon
confirming targets set in the PMTCT and EID tabs, return to the
**PMTCT_HEI_POS Linked to ART (FY22)** column in this section to review
ART targets for infants. Because HEI_POS targets are set without
disaggregation by sex, these are allocated equally to male and female
infants in the Cascade tab.

Because all infants in the previous year's Treatment cohort will
entirely shift into the 1-4 year old age group, both TX_NET_NEW and
TX_CURR for infants will reflect 100% of the value in the
**PMTCT_HEI_POS Linked to ART (FY22)** column.

## Cascade: TX_CURR_SUBNAT

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-TX_CURR_SUBNAT-BT-BV-1-1", "latex")

```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-TX_CURR_SUBNAT-BT-BV-1-1", "html")

```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **TX_CURR_SUBNAT (FY23)** $TX\_CURR\_SUBNAT.T$

### Instructions

1.  For ages one and older:

## Cascade: PEPFAR Testing

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-Testing-BW-CA-1-3", "latex")

schema_table("Cascade-Testing-CB-CE-2-3", "latex")

schema_table("Cascade-Testing-CF-CI-3-3", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-Testing-BW-CI-1-1", "html")
```

### DATIM Import

There are no Targets from this section that will be imported into DATIM.

### Instructions

1.  Review TX_NEW from Previously Diagnosed and adjust as appropriate.
    This is defaulted to 0%, reflecting an emphasis for Test and Start
    approaches for testing and linkage to treatment. Red highlights
    indicate percentages over 100%; yellow highlights indicate
    percentages changed from the default.

2.  Review the total TX_NEW from all other sources (FY22) for those to
    be linked to treatment from all HTS and EID testing modalities.

3.  Review observed ART Linkage Rate, based on FY20 Results reported in
    DATIM, for historical context.

4.  Review and adjust Targeted ART Linkage Rates for FY22. These are
    defaulted to 95%, but can be adjusted as necessary. Red highlights
    indicate percentages over 100%; yellow highlights indicate
    percentages below 95%.

5.  Review the Percent of HTS_TST_POS from HTS_INDEX from FY20 results,
    based on data reported in DATIM, for historical context.

6.  Review and adjust Targeted % of HTS_TST_POS from HTS_INDEX for FY22.
    These are set based on FY21 ART Coverage, per COP 21 Guidance, but
    can be altered as needed. Red highlights indicate percentages above
    100%; yellow highlights indicate percentages below thresholds
    stipulated in COP 21 Guidance. See below for additional information.

7.  Review total testing targets (HTS_TST_POS + PMTCT_HEI_POS) for FY22.
    Where necessary, return to previous assumptions and adjust
    appropriately.

8.  Review total Index testing targets (HTS_INDEX) for FY22 and adjust
    the Targeted % of HTS_TST_POS from HTX_INDEX for FY22 as necessary.

9.  Review FY22 targets for PMTCT_STAT New Positives and HTS_TST Post
    ANC1 New Positives and navigate to the PMTCT tab to adjust
    underlying assumptions as necessary.

10. Review FY22 targets for TB_STAT New Positives and navigate to the TB
    tab to adjust underlying assumptions as necessary.

11. Review FY22 targets for VMMC_CIRC Tested Positives and navigate to
    the VMMC tab to adjust underlying assumptions as necessary.

12. Review FY22 targets for PMTCT_HEI_POS and navigate to the EID tab to
    adjust underlying assumptions as necessary. For infants under 1 year
    old, 100% of testing targets should come through PMTCT_HEI_POS. See
    below for additional information.

13. Review FY22 targets for HTS_TST_POS from All Other Modalities and
    navigate to the HTS tab to adjust underlying assumptions as
    necessary.

14. Review percentage contributions toward FY22 targeted Total Positives
    from HTS_INDEX, PMTCT ANC1, PMTCT Post ANC1, TB_STAT, VMMC,
    PMTCT_HEI_POS, and All Other Modalities. Red highlights across these
    columns indicate cases where targets have been over- or
    under-distributed across modalities. See below for additional
    information about reconciling discrepancies among these modalities.

### Targeted % of HTS_TST_POS from HTS_INDEX

Per COP 21 Guidance, the total number of positives targeted to be
identified through Index Testing is initially modeled based on FY21 ART
Coverage as follows:

-   **ART Coverage \< 70%:** 30% of total positives to be identified
    through Index Testing

-   **ART Coverage >= 70% & \<80%:** 50% of total positives to be
    identified through Index Testing

-   **ART Coverage >= 80%:** 75% of total positives to be identified
    through Index Testing

In cases where historic FY20 results showed Index Testing contributing
to more than this share of testing, the larger value will be used.

Again, while modeled per the above, this value can adjusted as needed.

### Testing Rationalization

As testing targets are set in the PMTCT, TB, VMMC, and EID tabs, these
will be reflected here on the Cascade tab to reconcile against those
high-level testing targets set following the logic flow set forth in
preceding sections. This section of the Cascade tab can serve as a sort
of Table of Contents to help you navigate across these various tabs as
you adjust assumptions and reconcile targets. Similar Testing
Rationalization sections exist in each of these separate tabs for easier
reference.

Red highlighting will indicate any case where over- or
under-distribution of testing targets across testing modalities has
occurred, keying primarily from the Total Positives from All Other
Modalities (FY22) (%) column. As these issues arise, determine whether
these issues require adjustment of either preceding Treatment and total
Testing targets, or related targets in the PMTCT, TB, VMMC, or EID tabs.

After testing targets have been allocated to PMTCT ANC1, PMTCT Post
ANC1, TB_STAT, VMMC_CIRC, and PMTCT_HEI_POS, any remainder will be
available for further allocation against all remaining testing
modalities in the HTS tab of the Data Pack.

### Testing Targets for Infant Populations

Similar to targets for HIV-positive infants linked to ART as explained
above, targets for infants identified as HIV-positive are initially set
in the EID tab, without sex disaggregation. In reflecting these in the
Cascade tab, these values are equally allocated across male and female
infants.

Per COP 21 Guidance, 100% of these testing targets for infant
populations should be accommodated for via PMTCT_HEI_POS, and no other
modality. Should any portion of these targets be allocated to any other
modality, an alert will be flagged in the Data Pack Self-Service App.
Conditional formatting within the Data Pack will also indicate when this
has occurred.

## Cascade: Testing Reference Distribution

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-Testing Reference Distribution-CJ-CL-1-2", "latex")

schema_table("Cascade-Testing Reference Distribution-CM-CP-2-2", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-Testing Reference Distribution-CJ-CP-1-1", "html")
```

### DATIM Import

There are no Targets from this section that will be imported into DATIM.

### Instructions

1.  Review

## Cascade: HTS_Index

**HTS_INDEX:** Number of individuals who were identified and tested
using Index testing services and received their results

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-HTS_INDEX-CQ-CT-1-1", "latex")

schema_table("Cascade-HTS_INDEX-CU-CX-2-2", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-HTS_INDEX-CQ-CX-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **COMMUNITY - Contacts Tested, New Positive**
    $HTS\_INDEX\_COM.New.Pos.T$

-   **COMMUNITY - Contacts Tested, New Negative**
    $HTS\_INDEX\_COM.New.Neg.T$

-   **FACILITY - Contacts Tested, New Positive**
    $HTS\_INDEX\_FAC.New.Pos.T$

-   **FACILITY - Contacts Tested, New Negative**
    $HTS\_INDEX\_FAC.New.Neg.T$

### Instructions

1.  Review the estimated percent of total HTS_INDEX positives to be
    identified in Community Sites. This will initially be pre-populated
    based on FY20 results as recorded in DATIM, but may be adjusted as
    needed. Red highlights indicate percentages over 100%, or under 0%.

2.  Review estimated yields among HTS_INDEX contacts newly tested, both
    for those tested at Community sites, as well as for those tested in
    Facility sites. These are initially pre-populated based on FY20
    results from DATIM, but can be adjusted as needed. Red highlights
    indicate percentages over 100%, or under 0%; yellow highlights
    indicate cases where yield rates are less than 20% for 15+ year
    olds.

3.  Review modeled targets for the following columns. See below for
    additional information:

    a.  COMMUNITY -- Contacts Tested, New Positive

    b.  COMMUNITY -- Contacts Tested, New Negative

    c.  FACILITY-- Contacts Tested, New Positive

    d.  FACILITY-- Contacts Tested, New Negative

4.  Review the Actual percent of HTS_TST_POS to come from Index testing,
    calculated by dividing the sum of Community and Facility
    HTS_INDEX_POS by the total HTS_TST_POS.

### HTS_INDEX Disaggregates

In general, HTS_INDEX disaggregates across both Community and Facility
sites, and across both Negative and Positive HIV test results, are set
by combining HTS_INDEX_POS with the percentages set in steps 1 and 2
above.

FY22 targets for HTS_INDEX New Positives in Community Sites are set as
follows, rounding to the nearest integer:


\begin{center} ${HTS\_ INDEX\_ COM.New.Pos}_{t}\  = \ {HTS\_ INDEX.Pos}_{t}\  \times \ {\%\ HTS\_ INDEX\_ POS\ identified\ in\ Community\ Sites}_{t}$ \end{center}

Building from this, FY22 targets for HTS_INDEX New Negatives in
Community Sites are set as follows, rounding to the nearest integer:


\begin{center} ${HTS\_ INDEX\_ COM.New.Neg}_{t}\  = \ \frac{{HTS\_ INDEX\_ COM.New.Pos}_{t}}{\text{Community New Tested Yield}_{t}}\  - \ {HTS\_ INDEX\_ COM.New.Pos}_{t}$ \end{center}

Alternatively, FY22 targets for HTS_INDEX New Positives in Facility
Sites are set as follows, rounding to the nearest integer:


\begin{center} ${HTS\_ INDEX\_ FAC.New.Pos}_{t}\  = \ {HTS\_ INDEX\_ POS}_{t}\  - \ {HTS\_ INDEX\_ COM.New.Pos}_{t}$ \end{center}

And finally, FY22 targets for HTS_INDEX New Negatives in Community Sites
are set as follows:


\begin{center} ${HTS\_ INDEX\_ FAC.New.Neg}_{t}\  = \ \frac{{HTS\_ INDEX\_ FAC.New.Pos}_{t}}{\text{Facility New Tested Yield}_{t}}\  - \ {HTS\_ INDEX\_ FAC.New.Pos}_{t}$ \end{center}

## 

## Cascade: DIAGNOSED_SUBNAT

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Cascade-DIAGNOSED_SUBNAT-CY-CY-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Cascade-DIAGNOSED_SUBNAT-CY-CY-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **Host Country DIAGNOSED_SUBNAT (FY22)** $DIAGNOSED\_SUBNAT.T$

### Instructions

1.  Review and adjust the expected PEPFAR Coverage of Host Country Total
    Positives Identified for FY22. This is defaulted to match the PEPFAR
    Coverage of Host Country TX_NET_NEW_SUBNAT (FY22) set in the
    TX_NET_NEW_SUBNAT section of the Cascade tab, but can be altered as
    appropriate.

2.  Review FY22 targets for Host Country DIAGNOSED_SUBNAT. See below for
    additional information.

### DIAGNOSED_SUBNAT (FY22)

In conjunction with allowing import and update of FY21 targets in DATIM
for DIAGNOSED_SUBNAT, the Data Pack also allows import of FY22 targets
for this indicator. These are modeled within the Data Pack as follows,
rounded to the nearest integer:


\begin{center} ${DIAGNOSED\_ SUBNAT}_{t}\  = \ DIAGNOSED\_ SUBNAT.T\_ 1 + \ \frac{{HTS\_TST\_POS\  +  \ PMTCT\_ HEI\_ POS}_{t}}{\text{PEPFAR Coverage of Host Country Total Positives Identified}_{t}}$ \end{center}

Note that this modeling approach does not take into account mortality
rates among this population.

\elandscape

\newpage
