---
editor_options: 
  markdown: 
    wrap: 72
---

\blandscape

# PRIORITIZATION

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("Prioritization-Prioritization-B-D-1-1", "latex")

```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("Prioritization-Prioritization-B-D-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **SNU Prioritization (FY23)** \[IMPATT.PRIORITY_SNU.T\]

### Instructions

1.  Review the column "SNU Prioritization (FY21)" which will indicate
    prioritization levels set in COP22 for each PSNU.

2.  Review "SNU Prioritization (FY22)" and adjust as appropriate for
    COP21 programming. This is currently set to populate with the same
    level of prioritization that was referenced in step 1. Overwrite
    this column to set new levels of prioritization based on the list
    below. This column should only be populated using integers 1-8 and
    "M", "NA", or "Not a PSNU", as follows:

    a.  1 = "Scale-up: Saturation"

    b.  2 = "Scale-up: Aggressive"

    c.  4 = "Sustained"

    d.  5 = "Centrally Supported"

    e.  6 = "Sustained: Commodities"

    f.  7 = "Attained"

    g.  8 = "Not PEPFAR Supported"

    h.  "M" = "Military"

    i.  "NA","Not a PSNU" = "INVALID"

3.  Review the column "FY22 SNU Prioritization Translation" to ensure
    the prioritization level for each PSNU is correct. To make any
    changes, only edit the column "SNU Prioritization (FY23)" from
    Step 2.

\elandscape

\newpage
