\blandscape

# EID

## EID: PMTCT_EID (N)

**PMTCT_EID:** Number of infants who had a first virologic HIV test (sample collected) by 12 months of age during the reporting period.

```{r echo=FALSE, results='asis'}
sheet_name <- "EID"
section <- "PMTCT_EID (N)"
columns <- col_seq("C", "G")
data <- prepare_table_data(sheet_name, columns)
for (t in table_seq(data)) {
  make_table(t, section)
  }
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   ${\bf \leq 02 mo}$ $PMTCT\_EID.N.2.T$

-   ${\bf 02-12 mo}$ $PMTCT\_EID.N.12.T$

### Instructions

The PMTCT_EID indicator measures the extent to which HIV-exposed infants receive a first virologic HIV test to determine their HIV status by either 2 months or 12 months of age. Ideally, 80% of infants should be tested within the first two months, and 90-95% within the first twelve months.

1.  Review and adjust the assumptions for "Targeted % HIV exposed infants tested by 2 mo (%)" and "Targeted % HIV exposed infants tested by 12 mo (inclusive of tested by 2 mo) (%)". These will be set at a default of 95% and 95%, respectively. Red highlights indicate percentages over 100%; yellow highlights indicate percentages less than these default percentages.

2.  Review the Estimated number of infants born to HIV-positive women. In absence of granular, reliable, widespread data to estimate rates of multiple births, still births, or infant mortality, this statistic is approximated using the total number of HIV-positive women presenting to ANC (column "Total PMTCT: Positives (From ANC1 & Post ANC1)" of the PMTCT tab). For more information about the assumptions underlying this data, see the section of this User Guide about the PMTCT tab.

3.  Review modeled targets for "$\leq$ 02 mo" and "02 - 12 mo" PMTCT_EID, which are based on the proportions of HIV exposed infants (reflected in step 2) to be tested by 2 months and by 12 months (set in step 1). Return to steps 1 and 2 to make adjustments to the assumptions driving these two sets of targets.

## EID: PMTCT_HEI_POS (N)

**PMTCT_HEI_POS (N):** Number of HIV-infected infants identified in the reporting period, whose diagnostic sample was collected by 12 months of age.

```{r echo=FALSE, results='asis'}
sheet_name <- "EID"
section <- "PMTCT_EID (N)"
columns <- col_seq("H", "V")
data <- prepare_table_data(sheet_name, columns)
for (t in table_seq(data)) {
  make_table(t, section)
  }
```

### DATIM Import

No data points will be imported into DATIM from this section.

### Instructions

1.  For historical context, review FY21 results for Estimated Positivity Rates both for infants tested before 2 months old, and those tested between 2 and 12 months old. These data reflect data as reported currently in DATIM.

2.  Review and adjust assumptions for FY23 projections of Estimated Positivity Rates both for infants tested before 2 months old, and those tested between 2 and 12 months old. These data default to the same as those rates set in step 1, but can be adjusted as needed. Red highlights indicate percentages over 100% or less than 0%; yellow highlights indicate percentages that differ from those set in step 1.

3.  Review Targeted proportion of HIV-infected infants linked to ART. This rate is defaulted to 95%.

4.  Review Targeted TX Retention Rate (FY23) (%) which will default to 98%.

5.  Review Targeted % Eligible for VLS Testing (FY23) (%) which will default to 70%.

6.  Review Targeted % Eligible with Access to VLS Testing (FY23) (%) which will default to 100%.

7.  Review Targeted VL Suppression Rate (FY23) (%) which will default to 95%.

8.  Review "Total HIV infected infants identified" which will be the product of PMTCT_EID set in the previous section, multiplied by the Estimated Positivity Rates set in this section, summed across both PMTCT_EID age disaggregates. Please see below for a detailed formula of the calculation.

9.  Review "HIV+ infants linked to ART (FY23)" which is the product of "Total HIV infected infants identified" and Targeted ART Linkage Rate (FY23) (%)from Step 3. Adjust this value with column L. This will be referenced back to the Cascade tab for the \<01 age group.

10. Review "HIV+ infants retained on ART at end of FY23" which is the product of "HIV+ infants linked to ART (FY23)" and Targeted TX Retention Rate (FY23) (%) from Step 4. Adjust this value with column M. This will be referenced back to the Cascade tab for the \<01 age group.

11. Review "HIV+ infants tested for VLS (FY23)" which is the product of "HIV+ infants linked to ART (FY23)" with both Review Targeted % Eligible for VLS Testing (FY23) (%) from Step 5 and Targeted % Eligible with Access to VLS Testing (FY23) (%) from Step 6. Adjust this value with columns N and O. This will be referenced back to the Cascade tab for the \<01 age group.

12. Lastly, review "HIV+ infants Virally Suppressed (FY23)" which is the product of "HIV+ infants tested for VLS (FY23)" and Targeted VL Suppression Rate (FY23) (%) from Step 7. Adjust this value with columns P. This will be referenced back to the Cascade tab for the \<01 age group.

### PMTCT_HEI_POS (FY22)

To calculate the total number of HIV-infected infants to be tested and identified, the DataPack uses the following formula, rounding to the nearest integer:

$$
PMTCT\_ HEI\_ POS.T\  = \ (PMTCT\_ EID.N.2.T\  \times \ PMTCT\_ HEI\_ POS.2.Yield.T)\  +\\
\ (PMTCT\_ EID.N.12.T\  \times PMTCT\_ HEI\_ POS.12.Yield.T)
$$
\elandscape

\newpage
