---
editor_options: 
  markdown: 
    wrap: 72
---

\blandscape

# VMMC

## VMMC_CIRC_SUBNAT

```{r echo=FALSE, results='asis'}
sheet_name <- "VMMC"
section <- "VMMC_CIRC_SUBNAT"
columns <- col_seq("F", "R")
data <- prepare_table_data(sheet_name, columns)
for (t in table_seq(data, max_col = 3)) {
  make_table(t, section)
  }
```

### DATIM Import

The following data points will be imported into DATIM (only FY25 SUBNAT Targets) from this section:

-   **Host Country VMMC_CIRC_SUBNAT (FY24)** $VMMC\_CIRC\_SUBNAT.T\_1$

-   **Host Country VMMC_TOTALCIRC_SUBNAT (FY24)**
    $VMMC\_TOTALCIRC\_SUBNAT.T\_1$

-   **Targeted Host Country VMMC_TOTALCIRC_SUBNAT (FY25)**
    $VMMC\_TOTALCIRC\_SUBNAT.T$

-   **Targeted Host Country VMMC_CIRC_SUBNAT (FY25)**
    $VMMC\_CIRC\_SUBNAT.T$

### Instructions

1.  Review data for the following columns, all of which come from
    corollaries on the Cascade tab. Follow hyperlinks to navigate to the
    source of this data:

    a.  Host Country Estimated Male Population (FY24)

    b.  Host Country Estimated PLHIV (FY24)

    c.  Host Country Estimated HIV Prevalence (FY24)

    d.  Host Country Estimated TX_CURR_SUBNAT (FY24)

    e.  Host Country Estimated ART Coverage (FY24)


2.  If using Spectrum as the source for Host Country Context data, the
    following columns will initially be populated based on data from the
    Spectrum export dataset added to the Spectrum tab of the Target Setting Tool.
    Review these and return to Spectrum to adjust assumptions there as
    needed. With approval by your PPM and assigned DUIT Liaison, you may
    also identify and use another source for this data.

    a.  Host Country VMMC_CIRC_SUBNAT (FY24)

    b.  Host Country VMMC_TOTALCIRC_SUBNAT (FY24)

3.  Review Host Country Estimated VMMC Coverage (FY24), which is
    calculated by dividing the FY24 Host Country Estimated
    VMMC_TOTALCIRC_SUBNAT by the FY24 Host Country Estimated Male
    Population.

4.  Review Targeted Host Country VMMC Coverage (FY25), which is
    initially set to 80% per PEPFAR VMMC coverage goals, but you may
    adjust this based on PEPFAR Country-specific VMMC strategies and
    goals. Note that this statistic represents the targeted VMMC
    coverage to be achieved by October 2023.

5.  Review modeled FY25 targets for Host Country VMMC_TOTALCIRC_SUBNAT
    and VMMC_CIRC_SUBNAT. Return to steps 1-4 to adjust underlying
    assumptions as needed.

## VMMC: VMMC_CIRC

**VMMC_CIRC:** Number of males circumcised as part of the voluntary
medical male circumcision (VMMC) for HIV prevention program within the
reporting period.

**Note: For FY25 targets, males less than 15 years old will not be
eligible for PEPFAR-supported VMMC services.**

```{r echo=FALSE, results='asis'}
sheet_name <- "VMMC"
section <- "VMMC_CIRC"
columns <- col_seq("S", "AB")
data <- prepare_table_data(sheet_name, columns)
for (t in table_seq(data, max_col = 4)) {
  make_table(t, section)
  }
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   VMMC_CIRC Not Tested by PEPFAR (FY25) $VMMC\_CIRC.Unk.T$

-   VMMC_CIRC HIV Positive (FY25) $VMMC\_CIRC.Pos.T$

-   VMMC_CIRC HIV Negative (FY25) $VMMC\_CIRC.Neg.T$

### Instructions

1.  For historical context, review FY23 results and FY24 targets for
    PEPFAR VMMC_CIRC, supplied in the Target Setting Tool as an export from data
    currently reported in DATIM.

2.  Review the FY24 estimated PEPFAR Coverage of Host Country
    VMMC_CIRC_SUBNAT, calculated by dividing FY24 PEPFAR VMMC_CIRC
    targets by the projected FY23 Host Country VMMC_CIRC_SUBNAT.

3.  Review the FY25 PEPFAR coverage of Host Country VMMC_CIRC_SUBNAT,
    which is initially set equal to the FY24 estimated coverage rate set
    in step 2, but can be adjusted as needed.

4.  For Military SNUs only, adjust the FY24 to FY25 Change in VMMC_CIRC.
    For Military SNUs, this defaults to zero, but can be adjusted to
    match strategic programming as necessary.

5.  Review FY23 results for Observed Indeterminate/Not Tested Rate and
    Observed Positivity Rate among those VMMC clients newly tested for
    HIV, both of which are obtained from DATIM.

6.  Review and adjust FY25 projections for Estimated Indeterminate/Not
    Tested Rate and Estimated Positivity Rate among VMMC clients newly
    tested for HIV. Both of these estimates are initially set equal to
    their counterpart set in step 5, but can be adjusted as needed. Red
    highlights in either indicate percentages above 100% or below 0%;
    yellow highlights in the Estimated Positivity Rate column indicate
    yields greater than 1%.

7.  Review Targeted ART Linkage Rate for linkage between VMMC_CIRC: HIV
    Positive and TX_NEW. This rate is locked in step with ART Linkage
    Rates set on the Cascade Tab, which default to 95%; return to that
    tab to adjust this rate, though note that this will alter linkage
    rates across all modalities.

8.  Review modeled targets for Total VMMC_CIRC. See below for more
    information. Return to steps 1-4 and the previous section for
    VMMC_CIRC_SUBNAT to adjust assumptions driving this target.

9.  Review modeled targets for VMMC_CIRC Indeterminate/Note Tested, HIV
    Positive, and HIV Negative. See below for additional information
    about each of these.

10. Finally, review modeled data for those identified HIV positive via
    VMMC projected to be linked to ART, which is set by multiplying
    those identified HIV positive by the ART linkage rate reviewed in
    step 7.

### Total VMMC_CIRC (FY25)

For Military organization units, FY25 targets for Total VMMC_CIRC is set
as follows, rounding to the nearest integer:

$$
{VMMC\_ CIRC}_{t}\  = \ {VMMC\_ CIRC}_{t - 1}\  \times \ (1\  + \ {VMMC\_ CIRC.Change.Military}_{t})
$$

For all other organization units, FY25 targets for Total VMMC_CIRC are
set as follows, rounding to the nearest integer:

$$
{VMMC\_ CIRC}_{t}\  = \ {Targeted\ Host\ Country\ VMMC\_ CIRC\_ SUBNAT}_{t}\  \times \\
{PEPFAR\ Coverage\ of\ Host\ Country\ VMMC\_ CIRC\_ SUBNAT}_{t}
$$

### VMMC_CIRC Disaggregates (FY25)

In disaggregating total VMMC_CIRC for FY25 Targets, the Target Setting Tool will
first set targets for those projected to have indeterminate HIV testing
results or to deny testing, then targets for those identified positive,
and finally those negative.

To set targets for Indeterminate/Not Tested, the Target Setting Tool will use the
following formula, rounding to the nearest integer:

$$
{VMMC\_ CIRC.Unk}_{t}\  = \ {VMMC\_ CIRC}_{t}\  \times \ {Est.\ Indeterminate}/{Not\ Tested\ Rate}_{t}
$$

For VMMC_CIRC HIV Positive, the Target Setting Tool will set targets as follows,
rounding to the nearest integer:

$$
{VMMC\_ CIRC.Pos}_{t}\  = \ ({VMMC\_ CIRC}_{t}\  - \ {VMMC\_ CIRC.Unk}_{t})\  \times \ \text{Est. Positivity Rate}_{t}
$$

And finally, VMMC_CIRC HIV Negative targets will be set as a remainder
function, as follows:

$$
{VMMC\_ CIRC.Neg}_{t}\  = \ {VMMC\_ CIRC}_{t}\  - \ {VMMC\_ CIRC.Unk}_{t}\  - \ {VMMC\_ CIRC.Pos}_{t}
$$

## VMMC: Testing Rationalization

```{r echo=FALSE, results='asis'}
sheet_name <- "VMMC"
section <- "Testing Rationalization"
columns <- col_seq("AC", "AF")
data <- prepare_table_data(sheet_name, columns)
for (t in table_seq(data, max_col = 4)) {
  make_table(t, section)
  }
```

### DATIM Import

No data will be imported into DATIM from this section.

### Instructions

1.  Use this section of the VMMC tab to analyze how VMMC_CIRC HIV
    Positives fit within the context of an overall testing strategy. In
    particular, consider how this modality contributes to total
    HTS_TST_POS in relation to HTS_INDEX, TB_STAT, and all other HTS
    modalities.

2.  Review any cases where this section is highlighted red, indicating
    over- or under-allocation of HTS_TST_POS targets across contributing
    modalities. While these allocation issues may be more the result of
    a different modality(ies), analysis of these to confirm no
    adjustments to VMMC_CIRC are warranted may prevent issues and
    additional work in other sections of the Target Setting Tool.

3.  Return to other tabs of the Target Setting Tool where issues flagged in this
    section require adjustment of either total HTS_TST_POS targets, or
    targets via other modalities. Similar Testing Rationalization
    sections can be also found in each of these other tabs of the
    Target Setting Tool. You may also use hyperlinks in column headers in this
    section to quickly navigate to the most relevant section of the
    Target Setting Tool.

\elandscape

\newpage
