
\blandscape

PP
==

PP: PP_PREV
-----------

**PP_PREV:** Number of priority populations (PP) reached with the
standardized, evidence-based interventions (s) required that are
designed to promote the adoption of HIV prevention behaviors and service
uptake.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("PP-PP_PREV-F-H-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("PP-PP_PREV-F-H-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **PP_PREV (FY22)** [PP_PREV.T]

### Instructions

1.  "FY21 Targets\" column will come prepopulated with FY21 PP_PREV
    targets as currently reported in DATIM. Countries will review this
    data, but should not make changes to it. Though this column does not
    prevent users from making edits, teams must receive approval from
    their PPM and assigned DUIT Liaison before doing so. Changes made in
    this column will NOT be reflected in DATIM.

2.  Review and adjust the "Expected Change in PP_PREV services (%)".
    This defaults to 0%, though this reflects no suggestion of strategy
    from S/GAC. Adjust these growth rates to reflect intentional,
    data-driven, strategic programming. Values can be negative or
    positive percentages in this column, which will decrease or increase
    the FY22 target for PP_PREV respectively.

3.  "PP_PREV (FY22)" targets will be set as a growth rate function of
    the FY21 Targets and the Expected change % set in the previous two
    columns. To make changes to the COP21 target in this column,
    increase or decrease the Expected Change in PP_PREV services. In the
    case services are planned in FY22 where these were not provided in
    FY21, you may manually enter FY22 targets in these columns.
    
\elandscape

\newpage
