
\blandscape

CXCA
====

CXCA_SCRN
---------

**CXCA_SCRN (N):** Number of HIV-positive women on ART screened for
cervical cancer.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("CXCA-CXCA_SCRN-F-H-1-2", "latex")

schema_table("CXCA-CXCA_SCRN-I-K-2-2", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("CXCA-CXCA_SCRN-F-K-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **CXCA_SCRN** [CXCA_SCRN.T]

### Instructions

This indicator is **ONLY** **REQUIRED** for PEPFAR Cervical Cancer
Screening countries.

For countries that are **NOT REQUIRED** to report on this indicator, you
do not have to complete this section unless you plan to offer cervical
cancer-related services as per the relevant MER indicators. To remove
all cervical cancer targets, change the value in column "Targeted CXCA
Screening coverage rate (%)" to 0%.

1.  For historical context, review FY20 results, FY21 targets, and FY20
    Observed CXCA Screen Coverage rates as reported in DATIM, as well as
    FY22 Targets for TX_CURR from the Cascade tab of the Data Pack.

2.  Review and adjust Targeted CXCA Screening Coverage Rate (%). Column
    "Targeted CXCA Screening coverage rate (%)" will determine the
    proportion of HIV positive women currently on treatment that will
    receive cervical cancer screening in COP2120/FY21 implementation
    year. Each team will have a default value of 50% set in this column
    and should consult their S/GAC Chair or PPM when making adjustments.
    To remove all FY22 cervical cancer targets, set this column to 0%.

3.  Review FY22 targets for CXCA_SCRN and return to steps 1 and 2 to
    adjust. This target is set based on the number of eligible women in
    the COP 21 TX_CURR cohort multiplied by the Targeted CXCA Screening
    Coverage Rate.
    
\elandscape

\newpage
