---
editor_options: 
  markdown: 
    wrap: 72
---

\blandscape

# HTS_RECENT

**HTS_RECENT:** Number of newly diagnosed HIV-positive persons aged ≥ 15
years with a test for recent infection result during the reporting
period.

## HTS_TST Modalities

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("HTS_RECENT-Index (Community)-F-G-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("HTS_RECENT-Index (Community)-F-G-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   The **\# Tested for Recent Infection** Target for each modality.

### Instructions

1.  The HTS_RECENT Tab contains 15 different Modalities for both
    Facility and Community level targets. Each modality consist of two
    columns. The first column in each modality is the "% of Positives"
    for the specific modality indicator. Each of these columns is
    prepopulated with a default of 100% for each modality reflecting COP
    22 guidance that 100% of patients who test positive for HIV should
    also receive a recency test. These assumptions may be altered as
    needed by country teams, but they are conditionally formatted to
    highlight in Red should the percentage be over 100% and Yellow
    should they be less than 100%.

2.  Review the target column for each of these modalities will be set in
    the column "# Tested for Recent Infection" and will be a product of
    the "% of Positives" and the "Newly Tested, Positive" targets that
    were set in previous tabs that relate to each modality column.

3.  For example, the first Modality in this tab **PMTCT (Facilty)** will
    take the "% of Positives" and multiply it by the target that was set
    in column "Newly Tested, Positive" from the PMTCT tab. Each of the
    formulas that are prepopulated for each modality links back to the
    tab in which the main "Newly Tested, Positive" target was set. These
    reference tabs are: Cascade, PMTCT, TB, VMMC, and HTS.

## HTS_RECENT (Total)

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("HTS_RECENT-HTS_RECENT (Total)-AJ-AL-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("HTS_RECENT-HTS_RECENT (Total)-AJ-AL-1-1", "html")
```

### DATIM Import

No data points will be imported into DATIM from this section.

### Instructions

1.  Review "Total Recency Tests" column which is calculated by
    aggregating "# Tested for Recent Infection" across all modalities on
    the HTS_RECENT tab. To adjust individual targets by modality, return
    to the previous section. In some circumstances, it may also be
    necessary to return to the Cascade, PMTCT, TB, VMMC, or HTS tabs to
    adjust the number of HTS_TST_POS coming from each modality.

2.  Review "Total HTS_TST_POS" column which references "Final
    HTS_TST_POS" targets on the HTS tab. This column is here for
    reference only and should not be changed as changed in this column
    will not be reflected on the HTS tab and will not be imported into
    DATIM final targets.

3.  Finally, review the "Aggregate Recency Test Coverage Rate (%)"
    column to assess aggregate recency testing coverage across all
    modalities. If there are fewer recency tests done than there are
    HTS_TST_POS, or recency testing coverage is lower than 100%, then
    the column will be highlighted yellow. If this coverage is greater
    than 100% the cell will be highlighted Red.

\elandscape

\newpage
