
\blandscape

PrEP
====

PrEP: PrEP_NEW
--------------

**PrEP_NEW:** Number of individuals who have been newly enrolled on
antiretroviral pre-exposure prophylaxis (PrEP) to prevent HIV infection
in the reporting period.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("PrEP-PrEP_NEW-F-L-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("PrEP-PrEP_NEW-F-L-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **Newly on PrEP (FY22)** [PrEP_NEW.T]

### Instructions

1.  Review the PrEP_NEW section which will be populated with assumptions
    of FY22 Targets set at other points in the Data Pack for
    "HTS_TST_NEG", "Host Country Est. PLHIV", "AGYW(PREV (D)", and
    "AGYW_PREV (N)".

2.  Review data pulled from DATIM showing "PrEP_NEW (FY20 Results)", and
    "PrEP_NEW (FY21 Targets)".

3.  Manually enter targets for "Newly on PrEP (FY22)".

-   

PrEP: PrEP_CURR
---------------

**PrEP_CURR (N):** Number of individuals that received oral
antiretroviral pre-exposure prophylaxis (PrEP) during the reporting
period.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("PrEP-PrEP_CURR-M-O-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("PrEP-PrEP_CURR-M-O-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **Current on PrEP (FY22)** [PrEP_CURR.T]

### Instructions

1.  Review "PrEP_CURR (FY20 Results)" and "PrEP_CURR (FY21 Targets)",
    pulled from DATIM as a baseline in the FY22 target setting process.

2.  Similar to the process for setting FY22 PrEP_NEW targets, there is
    no pre-populated formula for FY22 PrEP_CURR targets. Manually enter
    these targets in this section based on calculations and strategic
    programming decided outside the Data Pack.
    
\elandscape

\newpage

