---
editor_options: 
  markdown: 
    wrap: 72
---

\blandscape

# OVC

## OVC: OVC_SERV

**OVC_SERV:** Number of beneficiaries served by PEPFAR OVC programs for
children and families affected by HIV.

```{r echo=FALSE, results='asis'}
sheet_name <- "OVC"
section <- "OVC_SERV"
columns <- col_seq("F", "S")
data <- prepare_table_data(sheet_name, columns)
for (t in table_seq(data)) {
  make_table(t, section)
  }
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **DREAMS** $OVC\_SERV.DREAMS.T$

-   **Preventive** $OVC\_SERV.Prev.T$

-   **Comprehensive -- Graduated** $OVC\_SERV.Grad.T$

-   **Comprehensive -- Active** $OVC\_SERV.Active.T$

### Instructions

1.  For historical context, review column "Host Country Est. PLHIV
    (FY22)", which will pull from the Cascade tab.

2.  Review the "DREAMS SNU?" column, which will indicate whether an SNU
    is actively implementing DREAMS activities by using "Y" for Yes and
    "N" for No. This column will come prepopulated based on the most
    up-to-date, authoritative list of DREAMS SNUs as centrally
    maintained by PEPFAR O/GAC. To add or remove any SNUs on this list
    during the COP21 process, notify your assigned PPM, as well as
    DREAMS liaisons on the PEPFAR Program Quality Team to ensure these
    changes are reflected in your DataPack. After communicating and
    documenting these updates centrally, the DataPack Self-Service App
    will alert to an update in the DREAMS SNU list and provide an
    updated DataPack with updated data in this "DREAMS SNU?" column.
    Note that in the interim, you may manually overwrite or alter flags
    in this column, though any discrepancies between this column in the
    DataPack and the centrally-maintained list of DREAMS SNUs will be
    flagged in the DataPack Self-Service App and must be resolved prior
    to COP Approval and DATIM import.

3.  Review columns "FY21 Results" and "FY22 Targets" which will come
    pre-populated with results and targets from DATIM and will serve as
    a baseline for COP21 target calculations.

4.  Review the column "Projected Net Change in OVC_SERV (%)", which will
    be preset with a default rate of 0%. Alter this percent value to
    either increase or decrease the OVC targets for COP21. Changes in
    this column will affect the overall OVC_SERV targets reflected in
    column "Total OVC_SERV".

5.  Review and adjust the allocation of total OVC_SERV across DREAMS,
    Preventive, and Comprehensive:

    a.  For DREAMS, allocations are only allowable where a district is
        denoted as a DREAMS SNU --- to adjust, return to step 2 --- and
        for females ages 10 to 17.

    b.  For Preventive services, allocations are only allowable for
        adolescents ages 5 to 14.

    c.  All remaining OVC_SERV is automatically allocated to the
        Comprehensive service category. Red highlighting in the column,
        Comprehensive % of Total OVC_SERV, indicates cases where
        percentages are over 100% or less 0%.

6.  Review and adjust the column "Targeted Graduation Rate among
    Comprehensive (%)", which is preset at a default value of 20%, per
    guidance from O/GAC. Adjust these values as necessary to align with
    the COP 2021 OVC strategy. Graduation rates can be set at any value
    between 0-100% but should not be a negative value. Red highlights
    indicate percentages over 100% or less than 0%; yellow highlights
    indicate graduation rates less than 20%.

7.  Review modeled targets for "Total OVC_SERV", which are calculated by
    applying the net rate of change decided in step 4 by the FY22 target
    referenced in step 3. In the case services are planned in FY23 where
    these were not provided in FY22, you may manually enter FY23 targets
    in this column.

8.  Review the number of OVC beneficiaries that are targeted by the
    DREAMS program COP21 implementation. This target is calculated by
    multiplying the total OVC_SERV target by the "Targeted DREAMS % of
    Total OVC_SERV (%) (FY23)" set in step 5. This formula is also
    dependent on the input into column "DREAMS SNU?", which must be
    marked with a "Y" to indicate the SNU is in fact a DREAMS SNU in
    order to set this target (see step 2).

9.  Review the number of OVC beneficiaries that are targeted by the OVC
    Preventive program COP21 implementation. This target is calculated
    by multiplying the total OVC_SERV target by the "Targeted Preventive
    % of Total OVC_SERV (%) (FY23)", set in step 5.

10. Review the number of OVC beneficiaries that are targeted for
    graduation from OVC Comprehensive services during COP21
    implementation. This target is a calculated by multiplying the Total
    OVC_SERV target by the "Targeted Comprehensive % of Total OVC_SERV
    (%) (FY23)" and "Targeted Graduation Rate among Comprehensive (%)
    (FY23)".

11. Review the targeted number of Active OVC Comprehensive beneficiaries
    for COP21. The Active OVC Comprehensive target is derived in the
    DataPack as a remainder of Total OVC_SERV to be served via
    Comprehensive services, less those captured in the "Comprehensive -
    Graduated" target. To make changes to "Comprehensive - Active"
    targets in the DataPack, adjust the proportion in the "Comprehensive
    % of Total OVC_SERV (%)" column, as set in step 5.

NOTE: There is no denominator for **OVC_SERV**

NOTE: Changing the values here will lead to downstream changes in
**OVC_HIVSTAT** column U.

NOTE: Column N Target % Graduation Rate **does not** include Exited or
Transferred Out in Denominator.

***\
***

## OVC: OVC_HIVSTAT

**OVC_HIVSTAT:** Number of orphans and vulnerable children (\<18 years
old) with HIV status reported, disaggregated by HIV status.

```{r echo=FALSE, results='asis'}
sheet_name <- "OVC"
section <- "OVC_HIVSTAT"
columns <- col_seq("T", "U")
data <- prepare_table_data(sheet_name, columns)
for (t in table_seq(data)) {
  make_table(t, section)
  }
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **\# OVC with reported HIV Status** $OVC\_HIVSTAT.T$ -- Note that
    this data will be aggregated across age group, resulting in one
    value per PSNU.

### Instructions

1.  Review the column "Targeted % OVC (\<18) with reported HIV Status
    (%) (FY23)" which is prepopulated at 100% by default, representing a
    goal of having 100% of those served via OVC Comprehensive services
    under 18 years old with reported HIV status. Adjust these values to
    either increase or decrease the COP22 target value in column "# OVC
    with reported HIV status". Red highlights indicate percentages
    greater than 100%, or less than 0%; yellow highlighting indicates
    percentages changed to less than 100%.

2.  Review the target value in column ""# OVC with reported HIV status
    (FY23)", which is calculated by multiplying those allocated to the
    OVC_SERV Comprehensive services disaggregates, whether Active or
    Graduated, and also less than 18 years of age. To adjust these
    targets, return to step 1.

\elandscape

\newpage
