---
editor_options: 
  markdown: 
    wrap: 72
---

\blandscape

# AGYW

This year's AGYW_PREV Tab is updated to incorporate results from the
DREAMS R-Shiny Saturation Application for OUs that choose to utilize it.
There are two paths an OU can take to generate COP24 AGYW_PREV Target
Thresholds -- Path 1 for those using outputs from the R-shiny App and
Path 2 for those not using outputs from the R-Shiny App. Targeting will
mirror the previous process.

```{r echo=FALSE, results='asis'}
sheet_name <- "AGYW"
section <- "AGYW_PREV"
columns <- col_seq("F", "S")
data <- prepare_table_data(sheet_name, columns)
for (t in table_seq(data, max_col = 4)) {
  make_table(t, section)
  }
```

**Column F Est. Female Population**

The R-Shiny App can be used to generate the AGYW population by 5-year
age bands in the absence of Spectrum data aggregated to the necessary
geographic level for the 25--29-year-old age band. The population data
source in the R-shiny App is from the US Census Bureau. **If your OU has
a different source you'd prefer, please provide the proper justification
to your DUIT Liaison during the Target Setting Tool Review.**

**Column G: H.C. Est \# of Vulnerable AGYW (FY24)**

-   Path 1: Please enter the estimated number of vulnerable (DREAMS
    eligible) AGYW by age/PSNU into the column from the R-Shiny App
-   Path 2: Estimate vulnerable AGYW by using =F\*Proxy Vulnerability
    Estimator
    -   Proxy Vulnerability Estimator is OUs estimate of \# of
        vulnerable/DREAMS eligible AGYW by age/geography.

**Column H: DREAMS Sat App Percent Coverage -- Saturation (%) FY23**

This is the estimated percent saturated. 
-   Path 1: This estimate can
come from the R-Shiny App output directly.
-   Path 2: If app is not used, in-country DREAMS databases can 
be utilized to determine this saturation percentage. The process 
of how this is done should be submitted as a narrative to DUIT Liaison

**Column I: DREAMS Sat App DREAMS Eligible Girls Not Yet Reached FY23**

-   Path 1: This column can be copied directly from the app.
-   Path 2: Populate this column with the following formula: $=(F*G*H)$.
    This will determine the number of DREAMS Eligible AGYW. *For both
    paths it is necessary to calculate this column.*

**Column J: Denominator - Started or Completed any DREAMS Service (FY24
Target)**

FY24 Targets for FY24 are pre-populated.

**Column K: Projected DREAMS Eligible Girls Not Yet Reached (FY25) -
Targeting Threshold**

This is the difference between Column I and Column J. It gives teams the
number of girls who have not yet been reached (either completed or
enrolled) into DREAMS services. This is the number of girls who can be
targeted within an OU. *For both paths it is necessary to calculate this
column.*

**Columns L -- Q: FY23 results across AGYW_PREV cascade. This is
pre-populated**

**Column R: Projected Net Change in Total AGYW_PREV from FY23 Results or
FY24 Targets (%)**

You will determine your projected net change from last year's results
(Column P). Over 100% is a targeted increase from Column P, and under
100% is a reduction from Column P.

**Column S: Targeted Percent Completion (FY25) (%)**\
This column will determine how many of the AGYW you plan to enroll into
DREAMS will complete the program based off her needs-profile. If the
completion rate from FY23 is over 60%, this column will mirror the
completion rate in column Q. If the completion rate from FY23 is under
60%, this column will default to 60%.

## AGYW: AGYW_PREV

**AGYW_PREV:** Number of active DREAMS beneficiaries that have started
or completed any DREAMS service/intervention as of the end of the
reporting period.

```{r echo=FALSE, results='asis'}
sheet_name <- "AGYW"
section <- "AGYW_PREV"
columns <- col_seq("T", "U")
data <- prepare_table_data(sheet_name, columns)
for (t in table_seq(data, max_col = 4)) {
  make_table(t, section)
  }
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **Denominator - Started or Completed any DREAMS Service**
    $AGYW\_PREV.D.T$

-   **Numerator - Completed at least Primary Package** $AGYW\_PREV.N.T$

### Instructions

1.  **Column T: Denominator - Started or Completed any DREAMS Service
    (FY25)**\
    This column determines your AGYW_PREV denominator. Please note --
    you will receive an error message if Column T \> Column K.

2.  **Column U: Numberator - Completed at least Primary Package
    (FY25)**\
    This is your numerator. The formula calculate the denominator
    (Column T) with the targeted percent completion (Column S).

\*Note: AGYW_PREV is reported by the USG team, not an IM, it doesn't
have to be assigned to an IM. It is automatically assigned to USG team,
and will not appear in the PSNUxIM tab for target allocation.

### AGYW_PREV Denominator (FY25)

FY24 targets for AGYW_PREV Denominator are set as follows, rounding to
the nearest integer:

$$
{AGYW\_ PREV.D}_{t}\  = \ {AGYW\_ PREV.D}_{r}\ *\\
(1\  + \ {Projected\ Net\ Change\ in\ Total\ AGYW\_ PREV}_{t})
$$

Note that neither this target nor the target for AGYW_PREV Numerator are
disaggregated by Service or Package Completion Status.

### AGYW_PREV Numerator (FY25)

FY25 Targets for AGYW_PREV Numerator are similarly modeled very simply
as follows, rounding to the nearest integer:

$$
{AGYW\_ PREV.N}_{t}\  = \ {AGYW\_ PREV.D}_{t}\ *\ \text{Targeted Percent Completion}_{t} 
$$ \elandscape

\newpage
