
\blandscape

AGYW
====

AGYW: AGYW_PREV
---------------

**AGYW_PREV:** Number of active DREAMS beneficiaries that have started
or completed any DREAMS service/intervention as of the end of the
reporting period.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("AGYW-AGYW_PREV-F-I-1-4", "latex")

schema_table("AGYW-AGYW_PREV-J-M-2-4", "latex")

schema_table("AGYW-AGYW_PREV-N-P-3-4", "latex")

schema_table("AGYW-AGYW_PREV-Q-S-4-4", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("AGYW-AGYW_PREV-F-S-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **Denominator - Started or Completed any DREAMS Service**
    [AGYW_PREV.D.T]

-   **Numerator - Completed at least Primary Package** [AGYW_PREV.N.T]

### Instructions

1.  For historical context, review Host Country Estimated Female
    Population for FY21, which is referenced from the Cascade tab.

2.  Enter values for the Host Country Estimated Number of Vulnerable
    AGYW projected as of September 2021, as available. These are for
    reference and not used to model targets in proceeding steps.

3.  For context, review FY22 targets for PrEP_NEW, PrEP_CURR, PP_PREV,
    and HTS_TST, set in other tabs of the Data Pack.

4.  For additional context, review FY20 results for AGYW_PREV and
    Observed Percent Completion as reported in DATIM.

5.  Review and adjust assumptions for Projected Net Change in Total
    AGYW_PREV from FY20 Results (%). This is defaulted to 0%, but can be
    adjusted as necessary. Red highlights indicate percentages over
    100%; yellow highlights indicate percentages less than 100% but not
    0%.

6.  Review and adjust assumptions for Targeted Percent Completion. This
    is defaulted to 60%, but can be adjusted as necessary. Red
    highlights indicate percentages over 100%; yellow highlights
    indicate percentages less than 60%.

7.  Review modeled FY22 targets for AGYW_PREV Denominator and Numerator,
    and return to steps 1-6 to adjust values as necessary. See below for
    additional information.

### AGYW_PREV Denominator (FY22)

As COP 21 represents the first year in which targets will be set for
AGYW_PREV, the process for arriving at these within the COP21 Data Pack
has been kept purposefully simple.

FY22 targets for AGYW_PREV Denominator are set as follows, rounding to
the nearest integer:

\begin{center} ${AGYW\_ PREV.D}_{t}\  = \ {AGYW\_ PREV.D}_{r}\ *\ (1\  + \ {Projected\ Net\ Change\ in\ Total\ AGYW\_ PREV}_{t})$ \end{center}

Note that neither this target nor the target for AGYW_PREV Numerator are
disaggregated by Service or Package Completion Status.

### AGYW_PREV Numerator (FY22)

FY22 Targets for AGYW_PREV Numerator are similarly modeled very simply
as follows, rounding to the nearest integer:

\begin{center} ${AGYW\_ PREV.N}_{t}\  = \ {AGYW\_ PREV.D}_{t}\ *\ \text{Targeted Percent Completion}_{t}$ \end{center}

\elandscape

\newpage
