---
editor_options: 
  markdown: 
    wrap: 72
---

\blandscape

# PrEP

## PrEP: PrEP_NEW

**PrEP_NEW:** Number of individuals who have been newly enrolled on
antiretroviral pre-exposure prophylaxis (PrEP) to prevent HIV infection
in the reporting period.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("PrEP-PrEP_NEW-F-L-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("PrEP-PrEP_NEW-F-L-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **Newly on PrEP (FY23)** \[PrEP_NEW.T\]

### Instructions

1.  Think through population specific target of PrEP with in country
    data, and population specific targets for AGYW, KP, zero-discordant
    couples and other at risk group, in line with COP22 Guidance.

2.  Review the PrEP_NEW section which will be populated with assumptions
    of FY23 Targets set at other points in the Data Pack for
    "HTS_TST_NEG", "Host Country Est. PLHIV", "AGYW(PREV (D)", and
    "AGYW_PREV (N)". Also think through KP PrEP strategy and history.

3.  Review data pulled from DATIM showing "PrEP_NEW (FY21 Results)", and
    "PrEP_NEW (FY22 Targets)".

4.  Manually enter targets for "Newly on PrEP (FY23)".

## PrEP: PrEP_CT

**PrEP_CT:** Number of individuals, excluding those newly enrolled, that
return for a follow-up visit or re-initiation visit to receive
pre-exposure prophylaxis (PrEP) to prevent HIV during the reporting
period.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("PrEP-PrEP_CURR-M-O-1-1", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("PrEP-PrEP_CURR-M-O-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **PREP_CT Continuing on PrEP (FY23)** \[PrEP_CT.T\]

### Instructions

1.  Think through population specific target of PrEP with in country
    data, and population specific targets for AGYW, KP, zero-discordant
    couples and other at risk groups, in line with COP22 Guidance. For
    each of these populations think through how groups may continue to
    use PrEP and remain at risk, go off PrEP due to change in risk, or
    return to PrEP due to a change in risk. Note that PrEP_CT is a
    revised and different indicator from PrEP_CURR. While PrEP_CURR
    historical targets and results are provided for context and
    assistance, they do not necessarily provide direct insight into
    PrEP_CT targets.

2.  Manually enter targets for "PrEP_CT (FY23)".

\elandscape

\newpage
