---
editor_options: 
  markdown: 
    wrap: 72
---

\blandscape

# KP_MAT

**KP_MAT:** Number of people who inject drugs (PWID) on
medication-assisted therapy (MAT) for at least 6 months

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("KP_MAT-KP_MAT-E-H-1-1", "latex")

schema_table("KP_MAT-KP_MAT-I-K-2-2", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("KP_MAT-KP_MAT-E-K-1-1", "html")
```

### DATIM Import

The following data points will be imported into DATIM from this section:

-   **KP_MAT (FY23)** \[KP_MAT.T\]

-   **Host Country KP_MAT_SUBNAT (FY23)** \[KP_MAT_SUBNAT.T\]

### Instructions

1.  Enter values for column "Host Country Estimated KP_MAT_SUBNAT
    (FY22)", as available. Sources for this data should be approved by
    the PPM and DUIT Liaison assigned to your Country.

2.  Review "PEPFAR KP_MAT (FY22 Targets)", pulled from DATIM as
    reference for historical context.

3.  Review Observed PEPFAR Coverage of KP_MAT_SUBNAT (FY22 Targets),
    calculated by dividing FY22 PEPFAR KP_MAT targets by Host Country
    Estimated KP_MAT_SUBNAT (FY22).

4.  Review "Targeted PEPFAR Coverage of KP_MAT_SUBNAT (FY23) (%)" which
    will pull directly from the previous column for FY22 that was
    calculated in the last step, but you may edit this as needed.

5.  Review and adjust "Targeted Growth in KP_MAT (FY23) (%)". This will
    be prepopulated at 0%, but you may adjust this as needed.

6.  Review "KP_MAT (FY23)" which will be the product of "PEPFAR KP_MAT
    (FY22 Targets)" multiplied against "Targeted Growth in KP_MAT (FY23)
    (%)". In the case services are planned in FY23 where these were not
    provided in FY22, you may manually enter FY23 targets in these
    columns.

7.  Review "Host Country KP_MAT_SUBNAT (FY23)" and adjust previous
    assumptions as needed. The Data Pack will model these targets based
    upon FY23 PEPFAR KP_MAT targets and the Targeted PEPFAR Coverage of
    KP_MAT_SUBNAT (FY23) (%).

\elandscape

\newpage
