---
editor_options: 
  markdown: 
    wrap: 72
---

\blandscape

# KP Validation

Each section of the KP_Validation tab looks at each indicator that sets
a Key Population target to ensure the total for each of these Key
Population disaggregated targets does not exceed the total Female and
Male 15+ populations for each PSNU. Under each of these sections there
is conditional formatting that will highlight any of the "KP Targets
Validation" columns in red if those values exceed the Total Targets.

```{r echo=FALSE, include=knitr::is_latex_output()}
schema_table("KP Validation-PrEP_CT-C-F-1-2", "latex")

schema_table("KP Validation-PrEP_CT-G-J-2-2", "latex")
```

```{r echo=FALSE, include=knitr::is_html_output()}
schema_table("KP Validation-PrEP_CT-C-J-1-1", "html")
```

### DATIM Import

There are no data points that will be imported into DATIM from this tab.

### Instructions

For each section of this tab, follow the below steps:

1.  Review the Total Population targets in the "Female, 15+ (FY23)",
    "AGYW, 15+ (FY23)", and "Male, 15+ (FY23)" columns, which sum
    targets across all 15+ age groups from where these are set in
    previous tabs of the DataPack.

    a.  Note that for the PrEP_CT and PrEP_NEW sections, the summation
        is pulling age group totals from the PrEP tab, TX sections from
        the Cascade tab, and HTS Sections from the HTS tab. Return to
        those tabs to investigate and adjust values. Changes made in
        this section of the KP Validation tab WILL NOT affect actual
        targets set in those tabs.

    b.  **NOTE**: Confirm for PrEP indicators that DREAMS age groups are
        aligned between KP and Total Populations, and ensure there is
        sufficient excess to target AGYW demographics.

2.  Review each column of the KP Targets Validation section. Data for
    these columns come originally from the KP tab of the DataPack.
    Return to that tab to investigate and adjust values. Changes made in
    this section of the KP Validation tab WILL NOT affect actual targets
    in the KP tab.

3.  Review the "FSW" column and ensure the total in this column does not
    exceed the total target for "Female, 15+ (FY23)". Cases where this
    does occur will be highlighted red.

4.  Review the "MSM" column and ensure the total in this column does not
    exceed the total target for "Male, 15+ (FY23)". Cases where this
    does occur will be highlighted red.

5.  Review the final three columns "People in prisons and other enclosed
    settings", "PWID", and "TG" to ensure that the sum of these three
    columns does not exceed the remainder of KP's --- the remainder
    after subtracting the amounts targeted in the "FSW" and "MSM"
    columns. Cases where this does occur will be highlighted red.

\elandscape

\newpage
